{\centering\section*{Abstract}}
This project focuses on the development of a simple yet engaging action-based shooting game designed for Android and iOS platforms. The game revolves around a thrilling storyline where a player is tasked with eliminating terrorists who have occupied a facility and are preparing to manufacture nuclear weapons. Equipped with various weapons, the player must clear out the enemies and allow a team of scientists to retrieve the dangerous equipment and dismantle it. The game features two levels, each progressively challenging, incorporating a basic AI system that triggers enemy attacks when the player comes within proximity.\\

The development of this game was carried out using Unity Hub and Unity Engine, with C\# as the primary scripting language. Visual Studio Community was employed for code development and debugging. Unity Asset Store was utilized for game assets, while Git and GitHub facilitated version control and collaboration. The game is optimized for both Android and iOS devices, with future plans to integrate cloud-based services such as Firebase. Although it is currently a single-player game, the architecture allows for future scalability, including multiplayer modes and cloud support.\\

The game integrates a shop system where players can purchase weapons using in-game currency. Although communication with an external server is implemented for the shop system, there is no payment integration yet. The game’s inventory system stores player progress locally on the device, ensuring offline playability. While Firebase integration is planned for future updates, the current version remains single-player and operates without cloud-based services or CI/CD pipelines. This project aims to deliver a compact, action-packed mobile gaming experience with future scope for additional features like multiplayer and cloud-based support.