\chapter{System Design}

System design is the process of defining the \cite {hocking2022unity} architecture, components, modules, interfaces, and data for a software system to meet specified requirements.

System design involves defining the overall architecture, breaking down the system into components and modules. Architectural design establishes the high-level structure, relationships between components, and communication mechanisms within the system.

\section{Architecture Design}
\textbf{Architecture design} is an important phase in system development that defines the structure and organization of a system. It defines the overall framework that indicates how various components interact, ensuring that the system meets functional requirements and performs efficiently. The architecture serves as a blueprint, guiding developers throughout the implementation process and enabling scaling and maintenance.

\begin{itemize}
\item \textbf{Component Identification:} Defining the individual components that make up the system, such as modules, libraries, and services.
\item  \textbf{Interaction Patterns:} Specifying how these components communicate and collaborate, including protocols, data flow, and interfaces.
\item \textbf{Design Patterns:} Utilizing established design patterns to solve common problems in software architecture, promoting re-usability and clarity.
\item \textbf{Scalability and Performance:} Considering how the architecture will support future growth and maintain performance standards under varying loads.
\end{itemize}
\subsection{Architecture Design of Gaming System}
