\chapter{Implementation and Testing}
\subsection{Implementation Environment}
\subsubsection{Programming Tools:}
Unity Hub \& Unity Engine were used as primary development tools for the game, where game assets, scenes, physics and animations were handled.Visual Studio Community version was employed for scripting and debugging C\# scripts. It's integrated with Unity to manage game logic, AI, and player interactions.
The Unity Asset Store leveraged for acquiring free assets, such as character models, environments, and particle effects to enrich the game's visuals and functionalities.
\subsubsection{Repository Setup \& Version Control:}
Git \& GitHub was used as a version control system to track changes and maintain backups of the project. Branching and merging were used to implement new features without affecting the main build.
\subsubsection{Integration:}
The game integrated multiple components like 3D models from the Asset Store, sound assets, and physics libraries within Unity.
Testing \& Debugging was performed through Visual Studio and Unity’s built-in play testing features.
In Unity, the Play Mode allows you to run the game within the Unity Editor itself. This lets you test the game in real time without needing to build and deploy it to a separate platform.
You can observe the game’s behavior, make changes to objects, scripts, and variables on the fly.
It helps in identifying issues such as gameplay bugs, AI behavior, and physics problems.
\subsubsection{Team Development Tools}
To make a plan and for easy management of the project, Trello was used.